### 2015-01-02 mcmc.tex
presenting results in high dimensions

% This file is part of the MCMC project,
%   which is part of the Data Analysis Recipes project
% Copyright 2013, 2014 David W. Hogg (NYU) and Dan Foreman-Mackey (NYU).

@@

...Now for multiple dimensions...return to the marginalization point
from above...

...What do you do in high-dimensional spaces?  Note the issue
that---even in a unimodal posterior PDF---the most probable model
might not be at the set of parameter values that are reported if you
compute the parameter values to report in one-dimensional projections
of the posterior pdf.  This requires a figure to demonstrate.  What to
do here?

...What figures should you make to display the chain?

...If you are really good, you will pass forward a sampling.
...How big should it be? Refer to Mackay here.
...Usefulness of a big sampling for hierarchical inferences; concept of interim prior?

>>>>

% This file is part of the MCMC project,
%   which is part of the Data Analysis Recipes project
% Copyright 2013, 2014, 2015 David W. Hogg (NYU) and Dan Foreman-Mackey (NYU).

@@

The parameter space $\pars$ is usually multi-dimensional, and more
than one of those parameters is of interest.
In this case, the mean or median of sampling can be produced for each
dimension.
Because the sampling projected onto any dimension is a marginalization
of the posterior pdf, any such one-dimensional mean or median is the
mean or median of the marginalized posterior pdf.

There is one oddity to note here, as it catches many investigators by
surprise:
Even if the model is good and the posterior pdf is unimodal and well-behaved,
the median (or even mean) of the posterior pdf for each of parameters,
when taken together as a ``best-fit'' parameter vector $\theta^\ast$,
will not itself necessarily be a good fit to the data!
If there is substantial ``curvature'' to the pdf in the parameter
space, the mean or median of sampling does not necessarily lie at a
high-probability location of parameter space.
This may seem counterintuitive, but it is easy to see in the case of a
``banana-shaped'' posterior pdf.
This all relates to the fact that MCMC is not an optimizer, it is a
sampler.
It is important, when reporting the output of an MCMC run by giving
means or medians of the posterior PDF to remind the reder or user of
that output that it does not necessarily represent (collectively) a
good fit to the data; these outputs only give information that is
useful one parameter at a time.

In principle the only output from the sampling that safely gives both
probabilistic information about the result of the inference and also
good-fitting models is a few---randomly chosen---example samples.
We strongly recommend this\note{HOGG:  And we do this WHERE? Citation!};
in particular this is a better thing to do
than to give the ``best sample'', which isn't even guaranteed to be
near the bulk of the posterior pdf or the samples therefrom.

If you \emph{do} return posterior samples to your audience, how many
should you return?
There are only heuristic answers to this, but a guideline is that, if
you only care about a single (one-dimensional) parameter, you don't
need many samples; a dozen suffices to give you a reasonable posterior
pdf mean and variance.\note{HOGG cite Mackay.}
If you care about $K$ parameters or dimensions of the parameter space,
in general the need for samples grows exponentially (or perhaps even
factorially!) with the number of dimensions.\note{HOGG cite something.}
So if you have a ten-dimensional space, expect to be publishing your
samples in an electronic table on the web!
If you \emph{do} publish sufficient numbers of posterior samples, you
might find users who want to make serious use of them.\note{HOGG cite
  our importance-sampling papers with some explanation here.}

Of course figures are always better than tables, at least in the
printed form of scientific publications.
In a $D$-dimensional parameter space, we recommend plotting all $D$
one-dimensional sample histograms, on a pretty fine binning, and all
$D$-choose-2 two-dimensional histograms (scatter plots) to show the
low-level covariances and non-linearities.
If you are clever, all these plots can be arranged into a lovely and
informative triangle.\note{HOGG cite triangle.py and put an example in
  the note!}
These two-dimensional plots do not in any sense contain all the
information in the sampling!  However, they are remarkable for
locating expected and unexpected parameter relationships, and often
invaluable for suggesting re-parameterizations and transformations
that simplify your problem.
